Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-09 paper.tex
update refs, start fleshing out intro

\usepackage[acronym,toc]{glossaries}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{UW}{UW}{University of Wisconsin}
%\newacronym{<++>}{<++>}{<++>}
\makeglossaries

\usepackage{graphicx}
\usepackage[printwatermark]{xwatermark}
\usepackage{xcolor}
\usepackage{placeins}

\newwatermark[allpages,color=black!5,angle=45,scale=6,xpos=-40,ypos=40]{DRAFT}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Facility and Time Step Discretization Effects in Fuel Cycle Simulation}

\author{Robert~W.~Carlsen, Paul~P.H.~Wilson}

% Institutes of the authors
\institute{University of Wisconsin - Madison, Department of Nuclear Engineering and Engineering Physics, Madison, WI 53706}

% Information concerning the person submitting the manuscript
\submitter{Robert W. Carlsen}

\submitteraddress{229 N Midvale Blvd Apt 1, Madison, WI 53705}
\submitteremail{rwcarlsen@gmail.com}

@@

\usepackage{cite} % order citations correctly

\usepackage{float} % used to help position figures with the H modifier

%%%%%%%%%%%%% stuff for syntax highlighting and code blocks %%%%%%%%%%%%%%%%
\usepackage{listings} % for highlighted code blocks
\usepackage{color}

% create listings pkg definition of diff language
\lstdefinelanguage{diff}{
  morecomment=[l][\color{blue}]{@@},     % group identifier
  morecomment=[l][\color{red}]-,         % deleted lines
  morecomment=[l][\color{green}]+,       % added lines
  morecomment=[l][\color{magenta}]{---}, % Diff header lines (must appear after +,-)
  morecomment=[l][\color{magenta}]{+++},
}
\definecolor{bkggray}{rgb}{0.93,0.93,0.93}
\lstset{
    backgroundcolor=\color{bkggray}
}
%%%%%%%%%%% end stuff for syntax highlighting and code blocks %%%%%%%%%%%%%%

\usepackage{tabularx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{caption}
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}%{S$_\text{N}$}%{$S_N$}%
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\newcommand{\Class}[1] {\texttt{#1}}%
\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%
\date{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

One of the major motivations for the development of Cyclus was creating a
simulation environment that is more expressive and less limited than the more
traditional system dynamics based simulators. One of the defining differences
between these two modeling paradigms involves the discretization of
facilities. System dynamics simulators such as VISION simulate facility
"fleets". In system dynamics fleet-based modeling:

@@

Cyclus' agent-based architecture in concert with its dynamic resource exchange
has the ability to model fleet-based facilities.  However, Cyclus was designed
with the intent of modeling facilities individually with discrete flows. The
difference between these two modeling styles in terms of their affects on
output of fuel cycle simulators in general is currently unknown. This
analysis is designed to provide both quantitative and qualitative insight
about how fleet-based continuous flow models differ from individual facility
discrete flow models.

@@

This work investigates in detail differences between fleet vs. individual
reactor modeling and time step duration.

>>>>

%%%%%% acronyms %%%%%%
\usepackage[acronym,toc]{glossaries}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{UW}{UW}{University of Wisconsin}
%\newacronym{<++>}{<++>}{<++>}
\makeglossaries

\usepackage[printwatermark]{xwatermark}
\usepackage{xcolor}
\newwatermark[allpages,color=black!5,angle=45,scale=6,xpos=-40,ypos=40]{DRAFT}

%%%%%%%% cover info %%%%%%%%%%%%%%%
\title{Facility and Time Step Discretization Effects in Fuel Cycle Simulation}
\author{Robert~W.~Carlsen, Paul~P.H.~Wilson}

\institute{University of Wisconsin - Madison, Department of Nuclear Engineering and Engineering Physics, Madison, WI 53706}
\submitter{Robert W. Carlsen}
\submitteraddress{229 N Midvale Blvd Apt 1, Madison, WI 53705}
\submitteremail{rwcarlsen@gmail.com}

@@

%%%%%%%%% includes and commands %%%%%%%%%%

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{tabularx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cite} % order citations correctly
\usepackage{float} % used to help position figures with the H modifier

\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

One of the major motivations for the development of the Cyclus fuel cycle
simulator was creating a simulation environment that is more expressive than
more traditional fuel cycle simulators.  Cyclus was designed with a
plugin-style architecture that allows different models for facility types to
be swapped in and out trivially.  As a Cyclus simulation walks through each
time step, facilities engage in a market-like dynamic resource exchange (DRE).
They broadcast requests for material and suppliers respond with bids. The DRE
then creates a network flow problem that it optimizes to resolve which
transactions actually occur.  The plugin architecture combined with the DRE
creates a powerful and flexible environment for the natural comparison of
different modeling paradigms.

Traditionally, many fuel cycle simulators use a system dynamics approach
\cite{forrester_industrial_1961} to modeling. These simulators model several
"stocks" that have levels that change over time due to "flows" between them.
The flows are determined by an equation that is a function of the state of the
system (i.e.  the system's stocks and flows).  A modeled system is then solved
in discrete or continuous time depending on the limitations of the software
and constraints imposed by the model.  In system dynamics simulators, the
number of stocks and potential flows between them is generally a static
property of the modeled system, making it more difficult to swap different
reactor models in and out of the same scenario without wiring them into the
simulator manually.

System dynamics based fuel cycle simulators generally use a collection of
stocks to represent the state of groups of like facilities commonly referred
to as "fleets".  As the simulation steps through time, the levels of stocks
(e.g. reactor fresh fuel inventory, repository waste inventories, etc.) are
adjusted according to the calculated flow values.  The VISION simulator
\cite{jacobson_verifiable_2010} among others operates this way.  In
fleet-based modeling:

@@

Cyclus' agent-based architecture in concert with its dynamic resource exchange
has the ability to model fleet-based facilities.  However, Cyclus was designed
with the intent of modeling facilities individually with discrete flows
enabling the investigation of interesting real-world effects such as
competition, reactor cycle staggering, and individual reactor outages.  The
difference between these two modeling styles in terms of their affects on
output of fuel cycle simulators in general is currently unknown. This analysis
is designed to provide both quantitative and qualitative insight about how
fleet-based continuous flow models differ from individual facility discrete
flow models.

@@

This work investigates in detail differences between fleet vs. individual
reactor modeling together with variations in time step duration.
